---
title: "Analysis of RNAseq counts"
author: "Murray Cadzow"
date: "20/04/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}
# Let’s look at our dataset and perform some basic checks before we do a differential expression analysis.


fcData <- read.table('yeast_counts_all_chr.txt', sep='\t', header=TRUE)
fcData %>% head()


# Rename data columns to reflect group membership
names(fcData)[7:12] = c("WT1", "WT2", "WT3", "MT1", "MT2", "MT3")



# Extract count data
# Remove annotation columns
# Add row names
counts <- fcData[, 7:12]
rownames(counts) <- fcData$Geneid

# Log transformation (add 0.5 to avoid log(0) issues):
logCounts <- log2(as.matrix(counts) + 0.5)

```


This analysis will start to look at differential expression between the wild-type and mutant yeast strains.

There are 7120 genes (rows) that will be compared in order to establish if there has been differential expression. First, we shall take a look at the counts per gene.






```{r, echo = FALSE}
boxplot(as.matrix(counts) ~ col(counts), main = "Counts per Gene", xlab = "Strain", ylab = "Count")
```


The data is highly skewed which suggests a log transform would be useful. This will be done by adding 0.5 to the counts to prevent a log2(0) issue.



```{r}
boxplot(as.matrix(logCounts) ~ col(logCounts))
```

This has improved the visualisation of the data.
